---
title: "Twitter Sentiment Geographical Index"
author: "Angelo Marra"
date: '2022-09-21'
output: html_document
---
```{r, here-I-am, include=FALSE}
here::i_am(
  "Final_Project.Rmd"
)
```


# Introduction

## Data Set

The *Twitter Sentiment Geographical Index* data set is divided into several csv files containing subjective well-being scores from various geographic locations. The subjective well-being scores are also referred to as the *sentiment index* in the study.

 The data ranges from 2012 to 2021, and the sentiment index is stratified into four levels: 

* World
* Country
* State
* County

The data is extremely comprehensive; holding data from multiple countries from every continent.

The variables within the data set are as follows:

===== ===== ===== ===== ===== ===== ===== ===== ===== ===== ===== ===== ===== ===== ===== ===== ===== ===== =====

**DATE:** (Date) The date of the sentiment index

**NAME_0:** (String) The country name

**NAME_1:** (String) The state/province name

**NAME_2:** (String) The county/city name

**SCORE:** (Float) A float value between 0 and 1 representing the
sentiment index where 1 represents a positive sentiment and 0 represents
the negative sentiment.

**N**: (Int) The number of posts generated given the specific date


===== ===== ===== ===== ===== ===== ===== ===== ===== ===== ===== ===== ===== ===== ===== ===== ===== ===== =====

## Analysis Objectives

 My analysis objectives for this project are as follows:

* **1:** I want to compare subjective well-being between developed and undeveloped nations. I will initially do so through descriptive statistics of the mean sentiment index. Later on I will consider performing t-tests and chi-squared analysis comparing the scores of developed and developing nations.

* **2:** I will analyze the sentiment index for all of the states within the USA to gain an idea of which states' social media users have the highest level of subjective well-being. I plan on creating in-depth visualization for this part of the analysis, and I will determine if there are significant sentiment index differences between states by performing multiple proportions tests within R.

* **3:** I wish to experiment with visualization options within R and educate myself on editing figures and tables within R-Markdown. Because this data set not contain a large amount of variables, I believe that it will offer me a great opportunity to hone my figure and table-making skills, while simultaneously allowing me to focus on R-Markdown exploration. 


```{r, include = FALSE}
## This chunk of code loads packages intended to assist us complete our project##
library(dplyr) #For dataframe modification
library(table1) #For table creation
library(kableExtra) #For table creation
library(ggplot2) #For figure creation
```

## Load in Data - State - 2012
```{r}
#!   read project_data1 from output directory
project_data1 <- readRDS(
  here::here("output/project_data1.rds")
)
```
## Here is a look into the dataframe
```{r, echo=FALSE}
head(project_data1, 10)
```

## Table Creation
This table displays some descriptive statistics of the sentiment index from some Grecian states. This table was created using Table1.
```{r, echo=FALSE}
#Load in final table from project directory
final.table <- readRDS(
  here::here("output/final.table.rds")
)

#Visualize Table
final.table
```
Within this table we are able to see the Mean and Median Sentiment Index Scores across all observations separated by state. *Standard Deviation* is included in the *Mean* row, and the *Minimum and Maximum* sentiment index scores are included in the *Median* row. We may observe that the mean index scores seem to be relatively similar among all Grecian states.

## Figure Creation
This box plot displays the distribution of the sentiment index from each Grecian state in the data set. Additionally, outliers within the distribution are marked by a red asterisk. This plot was created using ggplot2.

```{r, echo=FALSE, fig.width=12, fig.height =8, fig.cap="Twitter Subjective Wellbeing - Greece"}
 #Load in final graph from project directory
final.graph <- readRDS(
  here::here("output/final.graph.rds")
)

final.graph
```
We observe from this figure that the distribution of the sentiment index is not very different amongst Grecian states. Although, we can observe that among all Grecian states, *Epirus and Western Macedonia* seems to have the most variability in its sentiment index distribution, despite the fact that is has much less outlying data than other states.







